### 2019-02-09 ic-journal/unique.tex
Final fixes

For a system of rooted contractions, the meaning of 
``solution for $\rcontr$'' and of \emph{a unique solution for $\rapprox$}
is the expected one --- just replace in Def.~\ref{d:uniContra}  the preorder 
$\contr$ with $\rcontr$, and the equivalence 
$\approx$ with $\rapprox$ \DDS{ (note that  with $\rapprox$ one considers
solutions with respect to  $\rcontr$).}
%
For this new relation, the analogous of Lemma~\ref{l:uptocon} and of
Theorem~\ref{t:contraBisimulationU} can now be stated without constraints on the sum
operator.
The schema of the proofs is almost identical, because all 
properties of $\rcontr$ needed in this proof is its precongruence, which is
indeed true on unrestricted contexts including direct sums:
\begin{lemma}
\label{l:ruptocon}
Suppose $\til P$ and $\til Q$ are solutions  for $\rcontr$ 
 of a system of weakly-guarded
contractions.
For any context $\qct$, 
if  $\ct{\til P}\Arr{\mu}  R$,
 then 
there is a  context $\qctp$
such that $R \mcontrBIS \ctp{\til P}$ and  $\ct{\til Q} \Arr{\mu}
 \wb \ctp{\til Q}$.
\end{lemma}
The proof of Lemma~\ref{l:ruptocon} is exactly the same as of
Lemma~\ref{l:uptocon}, because all we need from $\mcontrBIS$ and
$\rcontr$ is their precongruences (in the sense of different
definitions of contexts). Also notice that, the conclusion of
Lemma~\ref{l:ruptocon} still uses $\mcontrBIS$, because $\rcontr$ does
not hold.

@@

\begin{proof}
\hl{Suppose $\til P$ and $\til Q$ are two such solutions: $\til P \rcontr
C[{\til P}]$ and $\til Q \rcontr C[{\til Q}]$ (thus also $\til P \wb
C[{\til P}]$ and $\til Q \wb C[{\til Q}]$).} We first follow the same steps as in the proof of
Theorem~\ref{t:contraBisimulationU} to show that the following
relation is bisimulation 
\DDS{ (using 
Lemma~\ref{l:ruptocon}
in place of  Lemma~\ref{l:uptocon}):}
\begin{equation}
\label{eq:R2}
\R \DSdefi \{ 
(R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{ for some context
$\qct$} \} \enspace.
\end{equation}
\DDS{The property that $\R$ is a bisimulation  proves  $\til P$ and $\til Q$ bisimilar, i.e.,
  $\til P \wb \til Q$.  To further prove
$\til P \rapprox \til Q$, we  appeal to
Lemma~\ref{l:obsCongrByWeakBisim}. Thus it remains to show that, for 
any two process $P$ and $Q$ and action $\mu$, if $P \arr{\mu} P'$ then
there is $Q'$ such that $Q \Arr{\mu} Q'$  and
$P'\ \R\ Q'$ (and  the converse direction).  The prove for this
part is routine,  using 
Lemma 3.13 of \cite{Mil89},  reported as 
Lemma~\ref{lem:313} in Section~\ref{ss:part2} (the lemma is  also needed 
in  Milner's  proof of ``unique solution of equations for $\sim$'').}
\end{proof}

>>>>

For a system of rooted contractions, the meaning of 
``solution for $\rcontr$'' and of \emph{a unique solution for $\rapprox$}
is the expected one --- just replace in Def.~\ref{d:uniContra}  the preorder 
$\contr$ with $\rcontr$, and the equivalence 
$\approx$ with $\rapprox$ (note that with $\rapprox$ one considers
solutions with respect to  $\rcontr$).
%
For this new relation, the analogous of Lemma~\ref{l:uptocon} and of
Theorem~\ref{t:contraBisimulationU} can now be stated without constraints on the sum
operator.
The schema of the proofs is almost identical, because all 
properties of $\rcontr$ needed in this proof is its precongruence, which is
indeed true on unrestricted contexts including direct sums:
\begin{lemma}
\label{l:ruptocon}
Suppose $\til P$ and $\til Q$ are solutions  for $\rcontr$ 
 of a system of weakly-guarded
contractions.
For any context $\qct$, 
if  $\ct{\til P}\Arr{\mu}  R$,
 then 
there is a  context $\qctp$
such that $R \mcontrBIS \ctp{\til P}$ and  $\ct{\til Q} \Arr{\mu}
 \wb \ctp{\til Q}$.
\end{lemma}
The proof of Lemma~\ref{l:ruptocon} is exactly the same as of
Lemma~\ref{l:uptocon}, because all we need from $\mcontrBIS$ and
$\rcontr$ is their precongruences (in the sense of different
definitions of contexts). Also notice that, the conclusion of
Lemma~\ref{l:ruptocon} still uses $\mcontrBIS$, because $\rcontr$ does
not hold.

@@

\begin{proof}
Suppose $\til P$ and $\til Q$ are two such solutions: $\til P \rcontr
C[{\til P}]$ and $\til Q \rcontr C[{\til Q}]$ (thus also $\til P \wb
C[{\til P}]$ and $\til Q \wb C[{\til Q}]$). We first follow the same steps as in the proof of
Theorem~\ref{t:contraBisimulationU} to show that the following
relation is bisimulation 
(using 
Lemma~\ref{l:ruptocon}
in place of  Lemma~\ref{l:uptocon}):
\begin{equation}
\label{eq:R2}
\R \DSdefi \{ 
(R,S) \st R \wb \ct{\til P}, S \wb \ct{\til Q} \mbox{ for some context
$\qct$} \} \enspace.
\end{equation}
The property that $\R$ is a bisimulation  proves  $\til P$ and $\til Q$ bisimilar, i.e.,
  $\til P \wb \til Q$.  To further prove
$\til P \rapprox \til Q$, we  appeal to
Lemma~\ref{l:obsCongrByWeakBisim}. Thus it remains to show that, for 
any two process $P$ and $Q$ and action $\mu$, if $P \arr{\mu} P'$ then
there is $Q'$ such that $Q \Arr{\mu} Q'$  and
$P'\ \R\ Q'$ (and  the converse direction).  The prove for this
part is routine,  using 
Lemma 3.13 of \cite{Mil89},  reported as 
Lemma~\ref{lem:313} in Section~\ref{ss:part2} (the lemma is  also needed 
in  Milner's  proof of ``unique solution of equations for $\sim$'').
\end{proof}
